\large Feature and order manipulations in a free recall task affect memory for current and future lists

### 2023-11-22 paper/main.tex

\title{\Large Feature and order manipulations in a free recall task affect memory for current and future lists}

\author{Jeremy R. Manning\textsuperscript{1, *}, Emily C.
Whitaker\textsuperscript{1}, Paxton C. Fitzpatrick\textsuperscript{1},
\\Madeline R. Lee\textsuperscript{1}, Allison M. Frantz\textsuperscript{1},
Bryan J. Bollinger\textsuperscript{1},\\Darya Romanova\textsuperscript{1},
Campbell E. Field\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1,
2}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili
Interactive Labs\\\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}

@@

\begin{document}
\maketitle
\thispagestyle{empty}

@@

@@

Our experiment is a variant of the classic free recall paradigm that we term
``\textit{feature-rich free recall}.'' In feature-rich free recall,
participants study 16 lists, each comprised of 16 words that vary along a
number of stimulus dimensions (Fig.~\ref{fig:exp}). The stimulus dimensions
include two semantic features related to the \textit{meanings} of the words
(semantic category, referent object size), two lexicographic features related
to the \textit{letters} that make up the words (word length in number of
letters, identity of the word's first letter), and two visual features that are
independent of the words themselves (font color, presentation location). Each
list contains four words from each of four different semantic categories, with
two referent object sizes reflected across all of the words. After studying
each list, the participant attempts to recall as many words as they can from
that list, in any order they choose. Because each individual word is associated
with several well-defined (and quantifiable) features, and because each list
incorporates a diverse mix of feature values along each dimension, this allows
us to estimate which features participants are considering or leveraging in
organizing their memories.

@@

\subsection*{Author contributions}

\subsection*{Author note}

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at
https://github.com/ContextLab/FRFR-analyses. Code for running the non-adaptive
experimental conditions may be found at
https://github.com/Con\-text\-Lab/efficient-learning-code. Code for running the
adaptive experimental condition may be found at
https://github.com/ContextLab/adaptiveFR. We have also released an associated
Python toolbox for analyzing free recall data, which may be found at
https://cdl-quail.read\-the\-docs.io/\-en/\-latest.  Note that this study was not
preregistered.  Some of the ideas and data presented in this manuscript
were also presented at the Annual Meeting of the Society for Neuroscience (2017)
and the Context and Episodic Memory Symposium (2017).

\subsection*{Acknowledgements}

>>>>

\title{\large Feature and order manipulations in a free recall task affect memory for current and future lists}

\author{\small{Jeremy R. Manning\textsuperscript{1, *}}, \small{Emily C.
Whitaker\textsuperscript{1}}, \small{Paxton C. Fitzpatrick\textsuperscript{1}},
\\\small{Madeline R. Lee\textsuperscript{1}}, \small{Allison M. Frantz\textsuperscript{1}},
\small{Bryan J. Bollinger\textsuperscript{1}},\\\small{Darya Romanova\textsuperscript{1}},
\small{Campbell E. Field\textsuperscript{1}}, and \small{Andrew C. Heusser\textsuperscript{1,
2}}\\\small{\textsuperscript{1}Dartmouth College}\\\small{\textsuperscript{2}Akili
Interactive Labs}\\\small{\textsuperscript{*}Corresponding author:
jeremy.r.manning@dartmouth.edu}}

@@

\begin{document}
\begin{titlepage}
\singlespacing
\footnotesize
\maketitle
\thispagestyle{empty}

@@

\paragraph*{Author contributions.}

\paragraph*{Author note.}

All of the data analyzed in this manuscript, along with all of the code for
carrying out the analyses may be found at
https://github.com/ContextLab/FRFR-analyses. Note that this study was not
preregistered.  Some of the ideas and data presented in this manuscript
were also presented at the Annual Meeting of the Society for Neuroscience (2017)
and the Context and Episodic Memory Symposium (2017).

\paragraph*{Acknowledgements.}

\end{titlepage}

\normalsize

@@

Our experiment is a variant of the classic free recall paradigm that we term
``\textit{feature-rich free recall}.'' In feature-rich free recall,
participants study 16 lists, each comprised of 16 words that vary along a
number of stimulus dimensions (Fig.~\ref{fig:exp}). The stimulus dimensions
include two semantic features related to the \textit{meanings} of the words
(semantic category, referent object size), two lexicographic features related
to the \textit{letters} that make up the words (word length in number of
letters, identity of the word's first letter), and two visual features that are
independent of the words themselves (font color, presentation location). Each
list contains four words from each of four different semantic categories, with
two referent object sizes reflected across all of the words. After studying
each list, the participant attempts to recall as many words as they can from
that list, in any order they choose. Because each individual word is associated
with several well-defined (and quantifiable) features, and because each list
incorporates a diverse mix of feature values along each dimension, this allows
us to estimate which features participants are considering or leveraging in
organizing their memories.  Our study was approved by the Dartmouth College
Committee for the Protection of Human Subjects (CPHS) under a protocol titled
``\textit{Efficient Learning}.''

@@
